Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-05-07 reply_to_reviews.tex

\blue
\subsection{Big picture}
\subsubsection{Proper scoring rules}
As noted by the authors, proper scoring rules are a commonly used concept in evaluating probabilistic predictions. While probably familiar to a reasonable fraction of readers, I think there is also likely a reasonable set of readers who are not aware of these or are only vaguely aware of them. For this reason I think a little more general background would help. For example on line 38 after the ‘report their true belief about nature’ another sentence or two along the lines of

“For example, some methods of ‘scoring’ probabilistic predictions can be ‘gamed’ in the sense that forecasters can do better by reporting a probability distribution different to their best estimate. A proper scoring rule ensures that the expected score when reporting a distribution Q, as evaluated under their actual best estimate of the probability distribution P, is best when Q = P. Thus a proper scoring rule encourages a forecaster to provide ‘honest’ predictions."

In addition, I suspect there are a few readers (such as myself!) who are more familiar with more ‘basic’ scores such as e.g. logarithmic score or deviance (i.e. essentially the likelihood or related quantities). I spent a bit of time wondering about why these weren’t considered, especially as these avoid the scale issues at the centre of the present article. Such scores were only briefly considered in the discussion, in the second-to-last paragraph. I think it would be helpful to mention/emphasise up front some of these ‘classic’ scores that don’t have the same issues with scaling and then discuss why they aren’t used, e.g. due to ‘robustness’ or other issues (e.g. lack of full probability distributions from forecasts).

\black
The paragraph now reads:

Proper scoring rules are constructed such that they cannot be gamed, meaning that forecasters (anyone or anything that issues a forecast) are incentivised to report their true belief about the future. In expectation, a forecaster receives the best score if their forecast $F$ coincides with the data-generating distribution $G$, that is if $F = G$. Common proper scoring rules are the logarithmic score \citep{goodRationalDecisions1952} or the continuous ranked probability score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007}. The log score is the log-likelihood of the predictive density at the observed value and is scale-invariant under monotonous transformations. The log score does not suffer from the issues we address in this paper, but due to a number of reasons is not widely used in fields such as weather forecasting or epidemiology. For example, the log score becomes very unstable for outlier forecasts that assign low density to the observed outcome. It is also difficult to apply to forecasts of discrete quantities and doesn't work for forecasts in a quantile-based format. 
More common in epidemiology are the CRPS or its discrete equivalent, the ranked probability score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the weighted interval score ~\citep[WIS,][]{bracherEvaluatingEpidemicForecasts2021}.

\red
\subsubsection{Log vs other transformations}
The authors take the position that the log transformation is generally preferable for their use case, though they discuss and compare others. Relatedly, their arguments in terms of relative error also involve an essentially log-linear (i.e. log data + additive error) form which may be pragmatic but somewhat inelegant imo.

@@

\black
We added numbers to all equations. 
\textbf{I now numbered everything. Are we fine with that?}

\blue
The first equation (line 43) uses an unbolded indicator function which isn’t defined (this also appears in the same form in the third equation, line 99). The second equation in contrast uses bold and defines the indicator. The definition should be moved forward and a choice of bold or not made.

\black
We added the definition to equation 1 and used bold throughout the manuscript consistently.

\blue
I think the term ‘propriety’ (as in having the property of being proper) should either be explicitly defined or re-worded in terms of ‘being proper’.

\black
We reworded occurences of the term `propriety'.

\red
No reference is provided for the approximate variance-stabilising properties of the square root transformation.

\black
Johannes, do you have one available?

@@

\red
\section{Reviewer \#2}

\textbf{Summary}

This manuscript develops theory, interpretations, and intuition regarding evaluation metrics applied to strictly monotonic transformations of observations and forecasts, with focus on log, shifted log, sqrt, and shifted sqrt transformations, and details the application and impact of using a log1p transformation within an evaluation framework for COVID-19 forecasts.
The analysis is extensive and covers many facets of selecting and applying such transformations, providing great value. However, it
\begin{itemize}
    \item focuses on putting evaluations for different locations and times on an even scale, and does not directly answer the question of how to re-emphasize locations and times of import to forecast consumers, and
    \item the discussion of which locations and times forecasts consumers would want to emphasize seems incomplete.
\end{itemize}
The former point could be addressed by adding additional content regarding re-emphasis. The latter point could be addressed by studying what stakeholders want to emphasize and using that to make a recommendation for a particular transformation or transformation selection rule. Alternatively, both could be addressed simply by more explicitly and prominently noting that
\begin{itemize}
    \item when selecting a transformation, one should consider the desired emphasis, which is likely not an even scale for most/all predictions, and
    \item the “natural logarithm” / log1p selection is not meant as a recommendation but to enable demonstration.
\end{itemize}

\black
It feels to me rather clear in the paper that we're showing people options and try to give them the tools they need to make a decision for themselves. Also we do kind of recommend the natural log. Any thoughts here?

True we don't really answer how a forecast consumer could re-emphasise locations / times as they want. We kind of do with Figure SI.7 where we show what happens for different offsets. We're also not saying what emphasis consumers should care about. But then again should we aim to do that? 
Alternatively we could argue that the major point about the log is the growth rate and that the more similar weighting is more an icing of the cake and we are not primarily concerned with re-weighing times / locations.

\red
Additionally, any additional necessary/recommended elements of a scoring procedure should be noted more prominently (e.g., dealing with forecast missingness, outlying forecasts, outlying data, selecting a Box-Cox transformation, selecting a shift ($a$ value), etc.).

\black
Hm potentially an interesting point. At the moment the paper kind of assumes you know what you're doing and suggests to do it differently. One could I guess add a paragraph that walks through all the steps? Add it where? Maybe this should be done in another piece that talks about best practices?

\red

@@

\subsection{Major comments}
``Natural logarithm'', log1p, and log($a + x$) are conflated in several places, despite the discussion in Section 2.4 noting that this is an important distinction. The terminology should not be overloaded. (E.g., L20 ``Applying the log transformation''.)

\black
L20 refers to the abstract. I changed ``Applying the log transformation'' to ``Applying a transformation of log($x + 1$)''.

In a more principled sense I'm not sure overloading the terminology is that much of a problem, since we explicitly analyse that adding 1 doesn't make that much of difference. We could make it more explicit though.

\red
L18:
\begin{itemize}
    \item ``relative error'' --- Is this what stakeholders want? Or does it overemphasize low steady periods too much?
    \item ``under the assumption of quadratic mean-variance relationship'' --- And do we expect/observe this sort of relationship in epidemiological surveillance data? This reads more like an arbitrary assumption that will be taken instead of something that is examined in the manuscript. (From Section 3.3 it seems like the answer is ``roughly but not entirely''.)
    \item These points might be more simply resolved simply by revising L15 ``motivate''.
\end{itemize}
\black

Johannes: e.g., \url{https://www.pnas.org/doi/pdf/10.1073/pnas.2103302119} emphasizes that the use of MAPE is motivated by its straightforward interpretation. Can we find another example?

Nikos: Since this line is just referring to the abstract, I'm not sure what exactly to change there? Should we replace the word `motivate' with something else? With what?

@@

\red
L150: “it may be desirable” — Is it though? This seems unlikely. Stakeholders likely want to emphasize some locations and times over others, and would benefit from some rules about how to do so while maintaining propriety. (E.g., is scaling by some function of recent observations or the population size okay? Is scaling by the forecast or observed value okay? Or are we limited to monotonic transformations?)

\black
We think there is a case to be made that each forecast target should have a similar impact on the overall result of the evaluation. This is true if the goal of the evaluation is to find the best forecasting model for future use and if one assumes that the difficulty of the forecasting task is similar in different locations. Take for example two models that make independent forecasts for cases of COVID-19 in Germany, Luxembourg and Liechtenstein. CRPS scores on the natural scale would be dominated by the predictive performance in Germany. One model could be a lot better in Luxembourg and Liechtenstein and slightly worse in Germany and end up looking worse in terms of overall CRPS. However, it is unclear whether predictive performance in Germany really provides e.g. 100 times more information about how good a model is at predicting disease dynamics. If the question is which model to deploy in another location in the future, then it might be desirable to not have average scores be dominated by a single location.

We have updated the paragraph as such:

\textit{When evaluating models across sets of forecasting tasks, it may be desirable for each target to have a similar impact on the overall results. This is true if one assumes that forecasts for different targets provide similar amounts of information about how well a forecaster performs. Ideally, one would like the magnitude of the score to scale with the difficulty of the prediction tasks and the information that can be obtained about overall performance of the forecaster. In disease incidence forecasting, however, CRPS values on the natural scale typically scale with the order of magnitude of the quantity to be predicted. Average scores are then dominated by the results achieved for targets with high expected outcomes in a way that does not necessarily reflect the underlying predictive ability well.}

Regarding the question which transformations are permissible:

Johannes: scaling by recent observations is okay and in a way that's what we are doing with the log (very similar to scaling with last value).Scaling by population size is okay as mentioned in discussion. Scaling with forecast or observation is not okay (I could probably find examples for that).

Do we need to update anything in the manuscript?

@@

\red
L166: “a negative binomial distribution with size parameter $\theta$” — Is this realistic? If so, what’s the interpretation epidemiologically?

\black
Nikos: This is an illustrative example and is not meant to be completely realistic. Rather, the point is to illustrate that for observations which have a standard deviation that grows linearly with the mean, the log transformation can serve as a variance-stabilising transformation. However, negative binomial distributions / Poisson gamma mixtures have been used in the past to model epidemiological processes.

Endo et al. (https://pubmed.ncbi.nlm.nih.gov/32685698/ ) for example estimated that the distribution of COVID cases could be well described using a negative binomial distribution with size $\Theta = 0.1$. This is a much stronger overdispersion then what we use in our example. 
\textbf{I'm actually somewhat confused about this. I remember Johannes rejecting my initial $\Theta = 0.1$ because he thought it was unrealistic. Am I severely misunderstanding Akira's paper?}

Johannes: But we could argue via Poisson gamma mixture, similar to the model in \url{https://doi.org/10.1111/rssa.12974}

@@

\red
Figure 3: is a geometric distribution realistic for epidemiological surveillance data?

\black
Nikos: Again refer to Akira's paper?

Johannes: Agree that it is not. Could add something along the lines of ``this can happen in principle, but only in rather constructed cases, such as for the geometric distribution in Fig 3, which is unlikely to occur in an epi setting.

@@

\red
L236: “better able to illustrate the effects” — Why does this removal help illustrate the effects? Is such a removal procedure required to be able to apply this transformation approach at all? And if so, what are the requirements/considerations for such a removal procedure?

\black
We updated the paragraph as follows:

\textit{In addition, we filtered out erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table SI.2. Those few erroneous outlier forecasts had excessive influence on average scores and relative skill scores in a way that was not representative of normal model behaviour. We removed them here in order to better illustrate the effects of the log-transformation on scores that one would expect in a 'normal' scenario. In a regular forecast evaluation such outlier forecasts should of course not be removed and count towards overall model scores.}

@@

L244: “pairwise comparisons” — The necessity of using an approach to handle missingness when combining evaluations should be noted more prominently from the beginning. The same applies to the outlier removal (if necessary) and a value selection.

\black
I'm not sure where we should note this. This is already more or less the beginning of the example part. 
And for the theoretical part it's not that relevant, because missingness is somewhat independent of whether we transform forecasts.

We could add a sentence like "This transformation approach can be combined with approaches like pairwise comparisons that handle missingness"? earlier in the introduction?

\red
Figure 4: The data (not) selected seems to obscure the key period of predicting the start of a case wave, as we expect the CRPS of log data to emphasize missed case increase predictions there more heavily than the natural scale. Deaths are not a substitute because they have access to a leading indicator and the same sort of misses may not be observed. The evaluations here may also miss some overshooting of the case peak. Which rules from Table SI.2 are coming into play and why? Is there a more complete alternative example?

\black
The data that was removed here was data revisions. The omissions are not due to the forecasts removed by the filtering. We added two Figures in the SI to make that clearer.

\red
Table 1: The beta for cases and beta for deaths are both around 0.86 individually. But fit together they beta is 0.963; this appears due to trying to fit two different (difficulties of) tasks together that follow different trends, evident from the differing alpha values. A joint fit does not seem appropriate without allowing for a separate alpha per task type. The same thing can be said for the different horizons within cases\&deaths. The fits here seem to better support an argument for something between sd and log.

\black
Johannes to the rescue: Any ideas for a smart response?

\blue
L279: “higher scores for smaller forecast targets” — This seems undesirable, given argument of Bracher et al. 2021a. Perhaps some forecast consumers would be interested in quality of forecasts for locations with lower activity (e.g., policymakers for smaller populations), but very unlikely would they want to prioritize less-active times in general over more-active times.

\black 
We generally agree that giving higher weight to targets with lower incidences may be undesirable in many instances (one important exception is instances where times of low incidences are followed by upswings). Empirically, in our example, the additional weight given to smaller forecast targets on the log scale was rather small compared to the excessive weight given to larger forecast targets on the natural scale. However we agree that this is a trade-off. One potential avenue for future exploration might be a composite score that combines scores on the natural and on the log scale.

\subsection{Minor comments}

\blue
L12 “over space and time” — Which do stakeholders care most about?

\black
We think that this is entirely up to the stakeholders and may depend on the setting. We hope that the reasoning and trade-offs involved become sufficiently clear throughout the remainder of the paper.

\blue
L15 “log-transformed counts” — Immediately sounds problematic due to the possibility of 0 counts, without mention of a shift or threshold. Additionally, there is a truncated normal distribution in the mix; is it rounded to counts, or are these not all count data?

\black
We changed "log-transformed counts" to "log-transformed values" and updated the abstract to point out that we're applying a transformation of log($x + 1$) to our example data:

\textit{Applying a transformation of log(x + 1) to data and forecasts from the European COVID-19 Forecast Hub}

The truncated normal distribution used as an example in Figure 2 is based directly on samples from the normal distribution, so here no rounding was applied.

\blue
L23–L24 “more strongly emphasized”, “less severely penalized” — Could note that this is relative to evaluations on the natural scale (not relative to each other).

\black
Thank you for the suggestion. We updated the abstract as such:

\textit{Situations in which models missed the beginning of upward swings are more strongly emphasised while failing to predict a downturn following a peak is less severely penalised when scoring transformed forecasts as opposed to untransformed ones.}

\red
L24 “is only one” — Seems a bit too similar to “the only one”, “the only”, etc.

\black
We hope that the remainder makes it sufficiently clear that other transformations are possible.

\blue
L46 “WIS is an approximation of the CRPS” — Is it an approximation of CRPS itself or some (2x?) scaling?

\black
The weighted interval score can is a weighted sum of interval scores for the individual prediction intervals. When weighing the individual interval scores for the central $(1 − \alpha)$ prediction intervals by 
$w = \alpha / 2$ (which is generally standard), then the WIS converges exactly to the CRPS for an increasing number of equally spaced prediction intervals. 
\textbf{Proper scoring rule dragon, attack!}

\blue
L59 “strength” — The meaning of “strength” is nonintuitive without reading the citation and understanding the ties to multiplicative interventions on R and r (the latter of which seems unrealistic to achieve). Consider surrounding with quotes, explaining more/less, relating to growth per generation, etc.

\black
We updated the sentence to make this clearer. The new sentence is now:

\textit{The reproduction number $R$ describes the number of people each infected person is expected to infect in turn (irrespective of the time between infections) and therefore is a measure of the strength of epidemic growth. The growth rate $r$ describes the speed of epidemic growth.}

\blue
L60: “immunity” $\xrightarrow{}$ “population immunity”?

\black
We changed this to "population immunity" as suggested.

\red
L69: This might benefit from a short justification (e.g.,
$\left| \frac{x_t e^{(r_t + \epsilon) \Delta t} - x_t e^{r_t \Delta t}}{x_t e^{(r_t - \epsilon) \Delta t} - x_t e^{r_t \Delta t}} \right| = e^{\epsilon\Delta t}$)

\red
L70: Clarify: is this suggesting to make the forecasting targets themselves the result of applying some standardized growth rate estimator to current+future observations around the desired time period?

@@

L146: “$\Bar{\hat{r}}$” — Should be $\hat{\Bar{r}}$, or consider $\hat{\Bar{r}}_t$.

L158 “delta method” — Delta method would seem to also require the distribution to be somewhat tightly distributed, concentrated within a nearly-linear region of the transformation function. But putting significant mass on a wider range of values would also mean having non-negligible mass on negative values if “approximately normal”; it would not make sense to apply the logarithm or sqrt transformations in these cases. So perhaps the “tightly distributed” assumption can be taken. But this seems a bit nonobvious and a justification/application of the delta method would be helpful here.

L159 — Need to discuss / spell out the point of the above calculation (— that it is the same for all $\mu$, when paired with the same $c$?).

\blue
L168: “grows with the variance” — May read like this a linear growth. Consider “grows with the standard deviation”.

\black
We have modified the sentence, which now reads:

\textit{We see that when applying the CRPS on the natural scale, the expected CRPS grows as the variance of the predictive distribution (which is equal to the data-generating distribution for the ideal forecaster) increases.}

As the rest of the paragraph talks about the variance, we kept the word variance here as well.

\blue

@@

L180: “data-generating” — Consider “fitted”/“believed”.

\black
In this instance "data-generating" is correct, as this is about a general property of proper scoring rules. We changed the sentence slightly to make this clearer:

\textit{We computed expected CRPS values  for three different distributions, assuming an ideal forecaster with predictive distribution equal to the true underlying (data-generating) distribution.}

\red
L186: “incentivizes overconfident predictions” — Needs justifica- tion/citation/removal. This single example disproves propriety but doesn’t establish overconfidence as being encouraged in general.

\black
While not proved here this is a statement that holds generally. Johaaannes? Also maybe we need a reference for this...

\red
Figure 2: Were any zeros encountered for the negative binomial or Poisson distributions? Was a shifted log transformation used rather than an unshifted log transformation?

\black 
As indicated in the Figure legend ("Expected CRPS was computed on the natural scale (left), after applying a square-root transformation (middle), and after adding one and applying a log-transformation to the data (right)), we have added 1 before applying the log transformation to deal with zero values.

\red
L215: “is mainly driven” — Please add pointer to justification (e.g., Figure 7 / discussion).

\blue
L231: “only include models which” — Consider “only include the 7 models that”

\black
Thank you for the suggestion, we edited the text accordingly.

### 2023-06-06 main.tex
go through reviewer comments

Forecast evaluation is essential for the development of predictive epidemic models and can inform their use for public health decision-making. Common scores to evaluate epidemiological forecasts are the Continuous Ranked Probability Score (CRPS) and the Weighted Interval Score (WIS), which are both measures of the absolute distance between the forecast distribution and the observation. However, applying these scores directly to predicted and observed incidence counts may not be optimal due to the exponential nature of epidemic processes and the varying magnitudes of observed values across space and time. In this paper, we argue that transforming counts before applying scores such as the CRPS or WIS can effectively mitigate these difficulties and yield epidemiologically meaningful and easily interpretable results. We motivate the procedure threefold using the CRPS on log-transformed values as an example: Firstly, it can be interpreted as a probabilistic version of a relative error. Secondly, it reflects how well models predicted the time-varying epidemic growth rate. And lastly, using arguments on variance-stabilizing transformations, it can be shown that under the assumption of a quadratic mean-variance relationship, the logarithmic transformation leads to expected CRPS values which are independent of the order of magnitude of the predicted quantity. Applying a transformation of log(x + 1) to data and forecasts from the European COVID-19 Forecast Hub, we find that it changes model rankings regardless of stratification by forecast date, location or target types. Situations in which models missed the beginning of upward swings are more strongly emphasised while failing to predict a downturn following a peak is less severely penalised when scoring transformed forecasts as opposed to untransformed ones. We conclude that appropriate transformations, of which the natural logarithm is only one particularly attractive option, should be considered when assessing the performance of different models in the context of infectious disease incidence.
\end{abstract}

@@

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that they cannot be gamed, meaning that forecasters (anyone or anything that issues a forecast) are incentivised to report their true belief about the future. In expectation, a forecaster receives the best score if their forecast $F$ coincides with the data-generating distribution $G$, that is if $F = G$. Common proper scoring rules are the logarithmic score \citep{goodRationalDecisions1952} or the continuous ranked probability score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007}. The log score is the log-likelihood of the predictive density at the observed value and is scale-invariant under monotonous transformations. The log score does not suffer from the issues we address in this paper, but due to a number of reasons is not widely used in fields such as weather forecasting or epidemiology. For example, the log score becomes very unstable for outlier forecasts that assign low density to the observed outcome. It is also difficult to apply to forecasts of discrete quantities and doesn't work for forecasts in a quantile-based format. 
More common in epidemiology are the CRPS or its discrete equivalent, the ranked probability score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the weighted interval score ~\citep[WIS,][]{bracherEvaluatingEpidemicForecasts2021}. 
The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - \boldsymbol{1}(x \geq y) \right)^2 dx,
\end{equation}    
\end{linenomath*}
where $y$ is the true observed value, $F$ is the cumulative distribution function (CDF) of the predictive distribution, and $\boldsymbol{1}()$ is the indicator function. The CRPS can be understood as a generalisation of the absolute error to predictive distributions, and interpreted on the natural scale of the data. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in so-called COVID-19 Forecast Hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome, $K$ is the number of predictive quantiles provided and $\boldsymbol{1}()$ is the indicator function. The WIS can be decomposed into three components, dispersion, overprediction, underprediction, which reflect the width of the forecast and whether it was centred above or below the observed value. We show an alternative definition based on central prediction intervals in Section \ref{sec:alternative-wis} which illustrates this decomposition.

@@

If the mean-variance relationship is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F_{\log}$ the predictive distribution for $\log(Y)$, we can use the delta method to show that
\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.
\end{equation}
\end{linenomath*}
The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome.

@@

To strengthen our intuition on how transforming outcomes prior to applying the CRPS shifts the emphasis between targets with high and low expected outcomes, Figure \ref{fig:SIM-wis-state-size-mean} shows the expected CRPS of ideal forecasters under different mean-variance relationships and transformations. We consider a Poisson distribution where $\sigma^2 = \mu$, a negative binomial distribution with size parameter $\theta = 10$ and thus $\sigma^2 = \mu + \mu^2/10$, and a normal distribution with constant variance. We see that when applying the CRPS on the natural scale, the expected CRPS grows as the variance of the predictive distribution (which is equal to the data-generating distribution for the ideal forecaster) increases. The expected CRPS is constant only for the distribution with constant variance, and grows in $\mu$ for the other two. When applying a log-transformation first, the expected CRPS is almost independent of $\mu$ for the negative binomial distribution and large $\mu$, while smaller targets have higher expected CRPS in case of the Poisson distribution and the normal distribution with constant variance. When applying a square-root-transformation before the CRPS, the expected CRPS is independent of the mean for the Poisson-distribution, but not for the other two (with a positive relationship in the normal case and a negative one for the negative binomial). As can be seen in Figures \ref{fig:SIM-wis-state-size-mean} and \ref{fig:score-approx}, the approximations presented above work quite well for our simulated example.

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population \citep{abbottEvaluatingEpidemiologicallyMotivated2022}. 
We suggested using the natural logarithm as a variance-stabilising transformation (VST) for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$, or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations (potentially after standardising different scores to have the same mean and standard deviation). This would make it possible to create custom scores and allow forecast consumers to choose and assign explicit weights to different qualities of the forecasts they might care about.

>>>>

Forecast evaluation is essential for the development of predictive epidemic models and can inform their use for public health decision-making. Common scores to evaluate epidemiological forecasts are the Continuous Ranked Probability Score (CRPS) and the Weighted Interval Score (WIS), which are both measures of the absolute distance between the forecast distribution and the observation. However, applying these scores directly to predicted and observed incidence counts may not be optimal due to the exponential nature of epidemic processes and the varying magnitudes of observed values across space and time. In this paper, we argue that transforming counts before applying scores such as the CRPS or WIS can effectively mitigate these difficulties and yield epidemiologically meaningful and easily interpretable results. Using the CRPS on log-transformed values as an example, we list three attractive properties: Firstly, it can be interpreted as a probabilistic version of a relative error. Secondly, it reflects how well models predicted the time-varying epidemic growth rate. And lastly, using arguments on variance-stabilizing transformations, it can be shown that under the assumption of a quadratic mean-variance relationship, the logarithmic transformation leads to expected CRPS values which are independent of the order of magnitude of the predicted quantity. Applying a transformation of log(x + 1) to data and forecasts from the European COVID-19 Forecast Hub, we find that it changes model rankings regardless of stratification by forecast date, location or target types. Situations in which models missed the beginning of upward swings are more strongly emphasised while failing to predict a downturn following a peak is less severely penalised when scoring transformed forecasts as opposed to untransformed ones. We conclude that appropriate transformations, of which the natural logarithm is only one particularly attractive option, should be considered when assessing the performance of different models in the context of infectious disease incidence.
\end{abstract}

@@

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that they cannot be gamed, meaning that forecasters (anyone or anything that issues a forecast) are incentivised to report their true belief about the future. In expectation, a forecaster receives the best score if their forecast $F$ coincides with the data-generating distribution $G$, that is if $F = G$. Common proper scoring rules are the logarithmic or log score \citep{goodRationalDecisions1952} or the continuous ranked probability score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007}. The log score is the log-likelihood of the predictive density at the observed value and is scale-invariant under monotonous transformations. The log score does not suffer from the issues we address in this paper, but due to a number of reasons is not as widely used in fields such as weather forecasting or epidemiology (see e.g., \citealt{Johansson2019} for an exception). For example, the log score assigns particularly severe penalties to occasional misguided forecasts. This lack of robustness may limit its practical applicability \cite{bracherEvaluatingEpidemicForecasts2021}. Moreover, it is not easily applied to forecasts reported as samples or quantiles, as used in many recent disease forecasting efforts. 
For these reasons, the CRPS or its discrete equivalent, the ranked probability score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the weighted interval score ~\citep[WIS,][]{bracherEvaluatingEpidemicForecasts2021} are more commonly used in epidemiology.

The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - \boldsymbol{1}(x \geq y) \right)^2 dx,
\end{equation}    
\end{linenomath*}
where $y$ is the true observed value, $F$ is the cumulative distribution function (CDF) of the predictive distribution, and $\boldsymbol{1}()$ is the indicator function. The CRPS can be understood as a generalisation of the absolute error to predictive distributions, and interpreted on the natural scale of the data. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in so-called COVID-19 Forecast Hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome, $K$ is the number of predictive quantiles provided and $\boldsymbol{1}()$ is the indicator function. The WIS can be decomposed into three components, dispersion, overprediction, underprediction, which reflect the width of the forecast and whether it was centred above or below the observed value. We show an alternative definition based on central prediction intervals in Section \ref{sec:alternative-wis} which illustrates this decomposition.

@@

If the mean-variance relationship is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F_{\log}$ the predictive distribution for $\log(Y)$, we can use the delta method (a first-order Taylor approximation, see e.g., \cite{Dunn2018}), to show that
\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.
\end{equation}
\end{linenomath*}
The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome.

@@

To strengthen our intuition on how transforming outcomes prior to applying the CRPS shifts the emphasis between targets with high and low expected outcomes, Figure \ref{fig:SIM-wis-state-size-mean} shows the expected CRPS of ideal forecasters under different mean-variance relationships and transformations. We consider a Poisson distribution where $\sigma^2 = \mu$, a negative binomial distribution with size parameter $\theta = 10$ and thus $\sigma^2 = \mu + \mu^2/10$, and a normal distribution with constant variance. We see that when applying the CRPS on the natural scale, the expected CRPS grows monotonically as the variance of the predictive distribution (which is equal to the data-generating distribution for the ideal forecaster) increases. The expected CRPS is constant only for the distribution with constant variance, and grows in $\mu$ for the other two. When applying a log-transformation first, the expected CRPS is almost independent of $\mu$ for the negative binomial distribution and large $\mu$, while smaller targets have higher expected CRPS in case of the Poisson distribution and the normal distribution with constant variance. When applying a square-root-transformation before the CRPS, the expected CRPS is independent of the mean for the Poisson-distribution, but not for the other two (with a positive relationship in the normal case and a negative one for the negative binomial). As can be seen in Figures \ref{fig:SIM-wis-state-size-mean} and \ref{fig:score-approx}, the approximations presented above work quite well for our simulated example.

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population \citep{abbottEvaluatingEpidemiologicallyMotivated2022}. 
We suggested using the natural logarithm as a variance-stabilising transformation (VST) for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$, or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. Potentially, the variance stabilising time-series forecasting literature may be a useful source of other transformations for various forecast settings.
